\documentclass[a4paper, twoside]{report}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{enumitem}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

%% own packages
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{gensymb}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs}
\usepackage[titletoc]{appendix}
\usepackage{titlesec}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{placeins}
\usepackage{rotating}
\usepackage{pifont}
\usepackage{array}
\usepackage{mdframed}
\usepackage{lipsum}
\usepackage[utf8]{inputenc}
\usepackage[many]{tcolorbox}
\usepackage{varwidth}
\usepackage{cleveref}
\usepackage{colortbl}
\usepackage{array}
%\usepackage{breqn}

%% own settings
% article
\setlength{\parindent}{0pt}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
% remove Chapter number from header name
%\titleformat{\chapter}[display]
%  {\normalfont\bfseries}{}{0pt}{\Huge}

\setlist{nosep}
\setlist{nolistsep}
\setlist{topsep=-5px}

\def \hfillx {\hspace*{-\textwidth} \hfill}

\makeatletter
\newcommand*{\centerfloat}{%
  \parindent \z@
  \leftskip \z@ \@plus 1fil \@minus \textwidth
  \rightskip\leftskip
  \parfillskip \z@skip}
\makeatother

\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}

\newenvironment{tight_enumerate}{
\begin{enumerate}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
}{\end{enumerate}}

% math
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\argmax}[2]{\underset{#1}{\arg \max} \hspace{0.1cm} #2}
\newcommand{\argmin}[2]{\underset{#1}{\arg \min} \hspace{0.1cm} #2}

\newmdtheoremenv{theo}{Theorem}
\newmdtheoremenv{proof}{Proof}

% Theo
\tcbuselibrary{theorems}
\newtcbtheorem[number within=chapter, crefname={theorem}{theorems},Crefname={Theorem}{Theorems}]{Theo}{Theorem}%
%
{enhanced, frame empty, interior empty, arc=0mm,
coltitle=black, fonttitle=\bfseries, colbacktitle=white,
borderline={0.5mm}{0mm}{},%
attach boxed title to top center={yshift=\dimexpr-\tcboxedtitleheight/2},
boxed title style={boxrule=-1pt},varwidth boxed title,
fontupper=\itshape, }{Th}

\newtcbtheorem[no counter, crefname={proof}{Proofs},Crefname={Proof}{Proofs}]{Proof}{Proof}%
%
{enhanced, frame empty, interior empty, arc=0mm,
coltitle=black, fonttitle=\bfseries, colbacktitle=white,
borderline={0.5mm}{0mm}{},%
attach boxed title to top center={yshift=\dimexpr-\tcboxedtitleheight/2},
boxed title style={boxrule=-1pt},varwidth boxed title,
fontupper=\itshape, }{Pf}

\title{Global Way-point LSTM Planner: An Online Machine Learning Solution for Robotic Path Planning}
\author{Alexandru Iosif Toma}
% Update supervisor and other title stuff in title/title.tex

\begin{document}
\input{title/title.tex}

\newpage
\mbox{}
\newpage

\begin{abstract}

%The path planning problem has essential applications in physical autonomous systems, such as robots and self-driving cars. 
Path planners have indispensable applications in physical autonomous systems such as robots and self-driving cars, in which human intervention is not desirable: bomb defusing, search and rescue, large scale manufacturing, warehouse management and many more. However, some of the classic solutions satisfy only a subset of the real-world application requirements imposed by hardware limitations. The work from this report shows that by adopting a hybrid approach between classic solutions and Machine Learning methods, we can develop a path planning solution that has support for partial knowledge environments while theoretically satisfying the real-world constraints. We create a platform for testing and developing the proposed solution while offering support for \textit{ROS}, a defacto in robotic systems. We theoretically and empirically assess the performance of the proposed solution against the well-known pathfinding solution, A*. We prove that the proposed solution achieves theoretically lower average case time and space complexity and significantly reduces the memory load compared to A*. Moreover, we show that the proposed solution is robust to unknown environments by evaluating it on real-world occupancy grid maps. Lastly, we run the proposed solution on a real-world robot and show that it can find a reasonable path in partial knowledge environments in which offline solutions such as A* cannot.

%The work from this report showcases a new hybrid pathfinding algorithm between classic solutions and ML methods, the Global Way-point LSTM Planner.

%

\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}

I would like to thank my supervisor, Sajad Saeedi for offering continuous support and invaluable advice in regards to the project. I would like to thank my co-supervisor, Ronald Clark for motivating me to pursue different objectives. I would like to thank my second marker, Andrew Davison for inspiring me to address real-world robotic applications in the Interim Report. I would like to thank the Percepbot team for offering me the robot hardware for the real-world evaluation. I would like to thank my friends, Alexandru Dan and Andrei Isaila for proof-reading my report. Lastly, I would like to thank my parents and all my friends for their emotional support during my university years.

\end{abstract}

{
  \hypersetup{hidelinks}
  \tableofcontents
}
%\listoffigures %85
%\listoftables  %53

\setlength{\parskip}{\baselineskip}
\input{introduction/introduction.tex}
\input{literature_review/literature_review.tex}
\input{background/background.tex}
\input{simulator/simulator.tex}
\input{methods/methods.tex}
\input{evaluation/evaluation.tex}
\input{conclusion/conclusion.tex}

\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{ieeetr}
\bibliography{bibs/sample}

\input{appendix/appendix.tex}

\end{document}